Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2017-09-29 paper/aldebaran.tex
tidy introduction

As can be seen from the scaling relations, asteroseismology can provide constraint on Mass, Radius, and surface gravity if \Dnu, \numax, and \teff can be measured.  In practise, for the higher luminosity red giants it is more straight forward to measure \numax than \Dnu.  Typical values for \numax might range from $0.1$ to $20 \rm \mu Hz$ for the luminous giants and $20$ to $50 \rm \mu Hz$ for red giants with luminosities similar to the red clump .  For the same sets of stars, \Dnu would take ranges from $0.02$ to $3 \rm \mu Hz$ and $3$ to $7 \rm \mu Hz$ depending on stellar mass and \teff (or metallicity which is considered more fundamental) \citep[e.g.,][]{2011A&A...525L...9M, 2013A&A...559A.137M}.  Hence, \numax requires less frequency resolution than \Dnu to establish a good measurement.

>>>>

As can be seen from the scaling relations, asteroseismology can provide constraint on Mass, Radius, and surface gravity if \Dnu, \numax, and \teff can be measured.  In practise, for the higher luminosity red giants it is more straight forward to measure \numax than \Dnu.  Typical values for \numax might range from $0.1$ to $20 \rm\,\mu Hz$ for the luminous giants and $20$ to $50 \rm\,\mu Hz$ for red giants with luminosities similar to the red clump .  For the same sets of stars, \Dnu would take ranges from $0.02$ to $3 \rm \mu Hz$ and $3$ to $7 \rm \mu Hz$ depending on stellar mass and \teff (or metallicity which is considered more fundamental) \citep[e.g.,][]{2011A&A...525L...9M, 2013A&A...559A.137M}.  Hence, \numax requires less frequency resolution than \Dnu to establish a good measurement.
